target_offtarget

### 2025-01-21 manuscript_figures.Rmd
updating figures

#### Make plot
```{r}
ggplot() +
  geom_point(data = depths_reads_sub,
             mapping = aes(log_viral_load, log_depth, color = virus)) +
  geom_abline(data = lm_combined, aes(intercept = `(Intercept)`, slope = log_viral_load), linetype="dotted") +
  geom_text(data = lm_combined,
            colour = "black",
            aes(
              x = 4.7,
              y = 3,
              label = round(Coeff_x1, digits = 2)),
            size = 3) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(x = 4, 
                y = 3, 
                label = "Slope ="),
            size = 3) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(
              x = 4.7,
              y = 2,
              label = round(R2, digits = 2)),
            size = 3) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(x = 4, 
                y = 2, 
                label = "R2 ="),
            size = 3) +
  facet_wrap( ~ virus, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray"),
    axis.title.y = element_text(size = 10),
    legend.title = element_blank()
  ) +
  xlab("log10(Viral Load)") +
  ylab("log10(Mean Read Depth)") +
  scale_color_manual(values = cols) +
  guides(color = FALSE)

@@

ggsave("figures/manuscript_figure_2025/PDF/Figure_1.pdf",
       width = 7.5,
       height = 4)

ggsave("figures/manuscript_figure_2025/PNG/Figure_1.png",
       width = 7.5,
       height = 4)

@@

### Final plot
```{r}
ggarrange(
  pool_counts_sum,
  pool_norm1_sum,
  pool_norm2_sum,
  pool_depths_sum,
  nrow = 2,
  ncol = 2,
  common.legend = TRUE, 
  align = "hv"
)

>>>>

#### Make plot
```{r, message=FALSE, warning=FALSE, echo=FALSE}
ggplot() +
  geom_point(data = depths_reads_sub,
             mapping = aes(Viral.load, mean_depth, color = virus)) +
  geom_abline(data = lm_combined, aes(intercept = `(Intercept)`, slope = log_viral_load), linetype="dotted") +
  geom_text(data = lm_combined,
            colour = "black",
            aes(
              x = 6*10000,
              y = 2,
              label = round(Coeff_x1, digits = 2)),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(x = 1.5*10000, 
                y = 2, 
                label = "Slope ="),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(
              x = 6*10000,
              y = 6,
              label = round(R2, digits = 2)),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(x = 2*10000, 
                y = 6, 
                label = "R2 ="),
            size = 3.5) +
  facet_wrap( ~ virus, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray"),
    axis.title.y = element_text(size = 10),
    legend.title = element_blank()
  ) +
    xlab("Log (Viral load)") + 
  ylab("Log (Mean Read Depth)") +
  scale_color_manual(values = cols) +
  guides(color = FALSE) +
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_y_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

ggsave("figures/manuscript_figure_2025/PDF/Figure_1.pdf",
       width = 8,
       height = 5)

ggsave("figures/manuscript_figure_2025/PNG/Figure_1.png",
       width = 8,
       height = 5)

@@

### ***Final plot***
```{r}
ggarrange(
  pool_counts_sum,
  pool_norm1_sum,
  pool_norm2_sum,
  pool_depths_sum,
  nrow = 2,
  ncol = 2,
  common.legend = TRUE, 
  align = "hv"
)
